Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-11 paper/paper.Rmd
certainty discussion

Participants provided their level of certainty regarding their choice using a five point scale. 
Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
Figure. \ref{certainty} shows that the

@@

@@

The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.

## Anomolies

@@

One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.

```{r}
ggdraw() +
  draw_plot(rasterGrob(readPNG("figures/aus_nwse_6_hex.png")))
```

!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)

### Certainty

@@

The participants were trained using three displays. There were relatively simple lineups and are shown in Fig.XXX.

@@

The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure
\ref{fig:survey-demogs}.

@@

![The lineup of choropleth map displays hides a distribution that affects all capital cities.](figures/aus_cities_3_geo.png)

![The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.](figures/aus_cities_3_hex.png)

The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as map (3). This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.

@@

```{r demogs, results = "asis"}
# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

# Demographics of contributors
#dem_contribs %>% count(gender)
dem_contribs %>% ggplot() + geom_bar(aes(age))

dem_contribs %>% count(gender) %>% knitr::kable(format = "latex", booktabs = TRUE)

dem_contribs %>% count(education) %>% knitr::kable(format = "latex", booktabs = TRUE)
```

>>>>

Participants provided their level of certainty regarding their choice using a five point scale. 
Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
Figure. \ref{certainty} shows the amount of times participants provided each level of certainty. This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend. This shows overconfidence in their detection ability when using a choropleth map display. Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.

@@

Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
"Colour trend across the areas" was the most common selection for NW-SE trend displays.
The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
Due to the consisent colouring of rural areas in a choropleth display, the choice "All areas have similar colours" was most common reason. The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.

The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.
This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions. It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays. 
Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays. All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.

The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response.

@@

## Choices

@@

@@

The participants were trained using three displays. There were relatively simple lineups and are shown in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.

@@

The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.

@@

```{r cities-geo, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
```

```{r cities-hex, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_hex.png")))
```

The higher values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as map (3). This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons. For different reasons the participants were able to make the same correct choice.

@@

```{r demogs, results = "asis", fig.cap = "The distribution of age groups of pariticpants."}
# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

# Demographics of contributors
#dem_contribs %>% count(gender)
dem_contribs %>% ggplot() + geom_bar(aes(age))
```

```{r gender, results = "asis", fig.cap = "The amount of participants who identify themselves by the pronouns He and She."}
dem_contribs %>% mutate(Gender = gender) %>% 
  count(Gender, name = "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
```

```{r education, results = "asis", fig.cap = "The highest level of education acheived by the participants "}
dem_contribs %>%
  mutate(Education = factor(education, levels = c("High School", "Bach", "Masters"), labels = c("High School Diploma", "Bachelors Degree", "Masters Degree"))) %>% 
    count(Education, name =  "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
```

### 2020-01-11 paper/paper.tex
certainty discussion

@@

Certainty levels are measured on a five point scale---they are subjective
assessments by the participant `How certain are you about your choice?'.

@@

@@

The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.

\hypertarget{anomolies}{%
\subsection{Anomolies}\label{anomolies}}

@@

One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.

\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}

\begin{figure}
\centering
\includegraphics{figures/aus_nwse_6_hex.png}
\caption{``A North-West to South East trend was hidden in this lineup of hexagon tile map displays.''}
\end{figure}

\hypertarget{certainty-1}{%
\subsubsection{Certainty}\label{certainty-1}}

@@

The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Figure
\ref{fig:survey-demogs}.

@@

\begin{figure}
\centering
\includegraphics{figures/aus_cities_3_geo.png}
\caption{The lineup of choropleth map displays hides a distribution that affects all capital cities.}
\end{figure}

\begin{figure}
\centering
\includegraphics{figures/aus_cities_3_hex.png}
\caption{The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.}
\end{figure}

The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as map (3). This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.

@@

\includegraphics{paper_files/figure-latex/demogs-1.pdf}

\begin{tabular}{lr}
\toprule
gender & n\\
\midrule
He & 67\\
She & 25\\
\bottomrule
\end{tabular}

\begin{tabular}{lr}
\toprule
education & n\\
\midrule
Bach & 56\\
High School & 23\\
Masters & 13\\
\bottomrule
\end{tabular}

>>>>

Participants provided their level of certainty regarding their choice using a five point scale.
Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
assessment by the participant prompted by the question: `How certain are you about your choice?'.
Figure. \ref{certainty} shows the amount of times participants provided each level of certainty. This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend. This shows overconfidence in their detection ability when using a choropleth map display. Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.

@@

@@

Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
``Colour trend across the areas'' was the most common selection for NW-SE trend displays.
The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
Due to the consisent colouring of rural areas in a choropleth display, the choice ``All areas have similar colours'' was most common reason. The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.

The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
The hexagon tile map displays resulted in ``Clusters of colour'' as the most common choice made by participants.
This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions. It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays. All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.

The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.

@@

\hypertarget{choices}{%
\subsection{Choices}\label{choices}}

@@

@@

The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/cities-geo-1.pdf}
\caption{\label{fig:cities-geo}The lineup of choropleth map displays hides a distribution that affects all capital cities.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/cities-hex-1.pdf}
\caption{\label{fig:cities-hex}The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.}
\end{figure}

The higher values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as map (3). This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons. For different reasons the participants were able to make the same correct choice.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/demogs-1.pdf}
\caption{\label{fig:demogs}The distribution of age groups of pariticpants.}
\end{figure}

\begin{tabular}{lr}
\toprule
Gender & Amount\\
\midrule
He & 67\\
She & 25\\
\bottomrule
\end{tabular}

\begin{tabular}{lr}
\toprule
Education & Amount\\
\midrule
High School Diploma & 23\\
Bachelors Degree & 56\\
Masters Degree & 13\\
\bottomrule
\end{tabular}
